Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=16, fig.height=5, fig.show="hold"}
library(scales)
scientific_10 <- function(x) {
  parse(text=gsub("\\+", "", gsub("e", " %*% 10^", scientific_format()(x))))
}

>>>>

```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=5, fig.show="last"}
library(scales)
scientific_10 <- function(x) {
  parse(text=gsub("\\+", "", gsub("e", " %*% 10^", scientific_format()(x))))
}
